Parameterization of the responses of subarctic European vegetation to key environmental variables for ozone risk assessment

### 2022-05-30 VegOzone.tex
Fix equation

In the $\mathrm{DO_3SE}$ model, the stomatal flux $\Phi_\mathrm{sto}$ in Eq.~(\ref{eq:pod}) is a fraction of the total \chem{O_3} deposition flux. A standard resistance analogous approach \citep{AE:Wesely1989} is used to transport \chem{O_3} from the atmospheric reference height $h_0$ to the vegetated surface. The calculation of aerodynamic $R_a$ and quasi-laminar boundary layer resistance $R_b$ follow \citet{WASP:Simpson2003,ACP:Simpson2012}. The surface resistance $R_\mathrm{surf}$ consists of stomatal $r_\mathrm{sto}$ and non-stomatal canopy resistances that include external plant surfaces $r_\mathrm{ext}$, aerodynamic within-canopy $R_\mathrm{inc}$ and ground surfaces or soil resistances $R_\mathrm{gs}$ \citep{WASP:Simpson2003,ACP:Simpson2012}. Under the assumption that the ozone concentration \chem{[O_3]} at the top of the canopy represents a reasonable estimate of the concentration at the upper surface of the laminar layer for a sunlit upper canopy leaf, $r_\mathrm{sto}$ and $r_\mathrm{ext}$ are calculated per leaf/needle area (note lower case $r$).
%
\begin{equation}
  R_\mathrm{sur} = \frac{1}{\frac{\mathrm{LAI}}{r_\mathrm{sto}}+\frac{\mathrm{SAI}}{r_\mathrm{ext}}+\frac{1}{R_\mathrm{inc}+R_\mathrm{gs}}}
\end{equation}
%
Stomatal resistance $r_\mathrm{sto}$ is the inverse of stomatal conductance $g_\mathrm{sto}$ in Eq.~(\ref{eq:stomatal}). Accounting for these the effective stomatal flux $\Phi_\mathrm{sto}$ at the vegetation height $h$ is defined as
%
\begin{equation}
  \Phi_\mathrm{sto} = \chem{[O_3]}(h) \cdot g_\mathrm{sto}(h).
  \label{eq:flux_stomata}
\end{equation}
A linear gradient reducing \chem{[O_3]} from $h_0$ to $h$ was adopted in the $\mathrm{DO_3SE}$ model based on detailed transport studies using the chemical transport model EMEP \citep{ACP:Simpson2012,ICP:MappingManual2017}.

>>>>

In the $\mathrm{DO_3SE}$ model, the stomatal flux $\Phi_\mathrm{sto}$ in Eq.~(\ref{eq:pod}) is a fraction of the total \chem{O_3} deposition flux. A standard resistance analogous approach \citep{AE:Wesely1989} is used to transport \chem{O_3} from the atmospheric reference height $h_0$ to the vegetated surface. The calculation of aerodynamic $R_a$ and quasi-laminar boundary layer resistance $R_b$ follow \citet{WASP:Simpson2003,ACP:Simpson2012}. The surface resistance $R_\mathrm{surf}$ consists of stomatal $r_\mathrm{sto}$ and non-stomatal canopy resistances that include external plant surfaces $r_\mathrm{ext}$, aerodynamic within-canopy $R_\mathrm{inc}$ and ground surfaces or soil resistances $R_\mathrm{gs}$ \citep{WASP:Simpson2003,ACP:Simpson2012}. Under the assumption that the ozone concentration \chem{[O_3]} at the top of the canopy represents a reasonable estimate of the concentration at the upper surface of the laminar layer for a sunlit upper canopy leaf, $r_\mathrm{sto}$ and $r_\mathrm{ext}$ are calculated per leaf/needle area (note lower case $r$).
%
\begin{equation}
  R_\mathrm{sur} = \frac{1}{\frac{\mathrm{LAI}}{r_\mathrm{sto}}+\frac{\mathrm{SAI}}{r_\mathrm{ext}}+\frac{1}{R_\mathrm{inc}+R_\mathrm{gs}}}
\end{equation}
%
Stomatal resistance $r_\mathrm{sto}$ is the inverse of stomatal conductance $g_\mathrm{sto}$ in Eq.~(\ref{eq:stomatal}). Accounting for these the effective stomatal flux $\Phi_\mathrm{sto}$ at the vegetation height $h$ is defined as
%
\begin{equation}
  \Phi_\mathrm{sto} = \chem{[O_3]}(h) \cdot \frac{g_\mathrm{sto}}{g_\mathrm{sto}+g_\mathrm{ext}} \cdot \frac{1}{r_b+r_c}.
  \label{eq:flux_stomata}
\end{equation}
A linear gradient adjusting \chem{[O_3]} from $h_0$ to $h$ was adopted in the $\mathrm{DO_3SE}$ model based on detailed transport studies using the chemical transport model EMEP \citep{ACP:Simpson2012,ICP:MappingManual2017}.
